---
title: "Bioporongs"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Bioporongs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Bioporongs)
```

# Description of the Packages

### Function 1 - Random_DNA_seq
This function creates a random DNA sequence with a specific *sequence length*.

```{r}
#EXAMPLE
Random_DNA_seq(10)
```

This is the sequence that can then be used in the following function.


### Function 2 - dna2rna
This function takes a given *dna_seq* and returns its corresponding RNA sequence

```{r}
#EXAMPLE
dna2rna("ATGCGTACGTTAGCCGTAGCTTGAATGCTAGC")
```


### Function 3 - get_codons

This function divide a biological nucleic-acid sequences (DNA or RNA) and returns a list of the codons. The starting point can be modified with the argument *start*.

```{r}
#EXAMPLE
get_codons("ATGCGTACGTTAGCCGTAGCTTGAATGCTAGC", start = 3)
```

## Function 4 - aminoacid_sequence

This function gets the sequence of codons and returns the amino acid sequence translation

```{r}
#EXAMPLE
aminoacid_sequence(c("AUG", "UUU", "UUA", "UGG", "UCU"))
```

### Function 5 - 
